Traversing symmetric NAT with predictable port allocation

### 2014-07-16 NAT_paper_ACM_short.tex
added github link
almost there

\begin{figure}%[H]
{\scalebox{0.48}{\includegraphics[trim=40 0 0 0]{alg_1.pdf}}}
\caption{Algorithm evaluation in a simulation, $T=10~ms$. Number of a simulation rounds for one parameter setting is 1000.
 A, B, C correspond to the Algorithm I, II and III respectively.
 D, E correspond to the Algorithm IV with optimized $C(\lambda T)$ by an exhaustive search in D case, 
 in E case $C(\lambda T)$ is approximated by a polynomial.}
\label{fig:alg_eval}
\end{figure}

\begin{figure}%[H]
{\scalebox{0.48}{\includegraphics[trim=40 0 0 0]{alg_steps.pdf}}}
\caption{Steps of the algorithms needed to success on average with respect to $\lambda$. Algorithms denoted in a same way as in figure \ref{fig:alg_eval}.}
\label{fig:alg_steps}
\end{figure}

@@

We developed an application written in Python that simulates NAT and mentioned algorithms, computes
statistics for port distributions on NAT and simulates algorithms for different parameters. It
may be helpful for another researchers interested in this area so we published it in public domain
hosted on GitHub [URL:HERE].

@@

\par\smallskip
\noindent\textbf{Acknowledgement.} 
This work was supported by the Czech Science Foundation, project GAP202/11/0422. TODO: ACK netflow Vykopall

>>>>

\begin{figure}%[H]
{\scalebox{0.48}{\includegraphics[trim=40 20 0 0]{alg_1.pdf}}}
\caption{Algorithm evaluation in a simulation, $T=10~ms$. Number of a simulation rounds for one parameter setting is 1000.
 A, B, C correspond to the Algorithm I, II and III respectively.
 D, E correspond to the Algorithm IV with optimized $C(\lambda T)$ by an exhaustive search in D case, 
 in E case $C(\lambda T)$ is approximated by a polynomial.}
\label{fig:alg_eval}
\end{figure}

\begin{figure}%[H]
{\scalebox{0.48}{\includegraphics[trim=40 20 0 0]{alg_steps.pdf}}}
\caption{Steps of the algorithms needed to success on average with respect to $\lambda$. Algorithms denoted in a same way as in figure \ref{fig:alg_eval}.}
\label{fig:alg_steps}
\end{figure}

@@

We developed an application written in Python that simulates NAT and mentioned algorithms, computes
statistics for port distributions on NAT and simulates algorithms for different parameters. It
may be helpful for another researchers interested in this area so we published it in public domain
hosted on GitHub: \url{https://github.com/ph4r05/NATSimTools}.

@@

We believe that by removing unnecessary intermediate nodes from
the communication path we restrict the attack and failure surfaces and increase the communication reliability.
Communication paths get less complex, transparency increases and this all support a more natural way of the 
interconnecting nodes on P2P basis.

\par\smallskip
\noindent\textbf{Acknowledgement.} 
This work was supported by the Czech Science Foundation, project GAP202/11/0422. The netflow data was provided
by the CSIRT team of the Masaryk University, Brno, Czech Republic TODO: FIX.
